Normalized Coherence

### 2019-09-17 Analysis/Normalized_Coherence.Rmd
Code for generating random networks

>>>>

# Generating random networks for comparison to msigdf (Category_Tables)

```{r}
#Function for generating random networks from a set of sizes
#size_vec is vector of sizes

generate_rand_slopes = function(size_vec, database) {
  j=1
  slope_list = c()
  for (i in size_vec) {
    # Empty data frame for disease networks
      diseases = bind_rows()
      # Generate random networks until there as many internal edges as current diseases
      while(nrow(diseases)<i) {
        # Generate random diseases network from PPI database[??? What this function does?]
        diseases_curr = GeneSample(i, database, directed = FALSE) 
        # Save internal and external edges
        diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = diseases_curr$internal_connectivity, External = diseases_curr$external_connectivity)
        # Filter out zeros
        diseases_curr = diseases_curr %>% filter(Internal !=0) 
        # Bind together non-zero internal/external edges (If all zero then diseases_curr is null and nothing happens)
        diseases = bind_rows(diseases, diseases_curr)
      }
          # Save slope of current network
          slope_list= c(slope_list,coef(lm(I(sqrt(External)) ~ I(sqrt(Internal))-1, data = diseases))[[1]])
          # Iterate
          j = j+1

  }
  data.frame(Count = size_vec, Slope = slope_list)
}
```

```{r}
#Read in data if you only want to run this section

# msig_frame_string = readRDS("String_Msig_Slopes.rds")

#Get msig counts (Comment out if using pre-calculated msig slopes)

msig_counts = unique((msig_frame_string %>% filter(Category == "CP:KEGG"))$Num_Genes)

#Generate the random slopes equal to msig lengths
string_random = generate_rand_slopes(msig_counts, string)

 saveRDS(string_random, "./data/Coherence_Results/string_random_edges.rds")
```
